Reviewers Comments \& Authors Replies

### 2015-07-06 Report/wsrm_formulation.tex
half cooked

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let 
\begin{IEEEeqnarray}{l}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{IEEEeqnarray}
be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.

For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub
\end{IEEEeqnarray}
and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality
\iftoggle{single_column}{
\begin{IEEEeqnarray}{l} \label{eqn-8} \IEEEyesnumber
	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{IEEEeqnarray}
}{
\begin{multline}\label{eqn-8}
2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{multline}
}
In summary, for fixed linear receiver \me{\mvec{w}{l,k,n}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
\end{IEEEeqnarray}

Now, the optimal linear receivers for fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
\underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
\end{IEEEeqnarray}
Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{o}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
\end{IEEEeqnarray}
where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}. The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function. The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.

It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
\allowdisplaybreaks{
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
\end{IEEEeqnarray}}
Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.

The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved iteratively by updating the operating point from the previous iteration. The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}. \review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the chosen transmit precoders and the receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}. Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}. The iterative procedure is performed until convergence or for fixed number of iterations \me{I_{\max}} as shown in Algorithm \ref{algo-1}. The convergence analysis is given in Appendix \ref{sec-3.5}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
			$j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1}
\end{algorithm}

\begin{comment}
\subsubsection*{Convergence}
In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
\end{subeqnarray}
where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}. The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}. It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.

>>>>

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let 
\begin{IEEEeqnarray}{l}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{IEEEeqnarray}
be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.

For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub
\end{IEEEeqnarray}
and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality
\iftoggle{single_column}{
\begin{IEEEeqnarray}{l} \label{eqn-8} \IEEEyesnumber
	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{IEEEeqnarray}
}{
\begin{multline}\label{eqn-8}
2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{multline}
}
For a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n} = \{ \tilde{\mbf{m}}_{l,k,n},\tilde{\mbf{w}}_{l,k,n},\tilde{\mbf{\beta}}_{l,k,n} \}}, the relaxed convex subproblem is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
\underset{\substack{\mbf{m}, \mbfa{\gamma},\mbfa{\beta}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\tilde{\mbf{w}}_{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
\end{IEEEeqnarray}

Now, the optimal linear receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
\underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
\end{IEEEeqnarray}
Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{o}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} \tilde{\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} \tilde{\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} \tilde{\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} \tilde{\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
\end{IEEEeqnarray}
where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}. The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function. The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.

It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
\allowdisplaybreaks{
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} \tilde{\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \tilde{\mbf{m}}_{l,k,n}. \IEEEyessubnumber \label{eqn-10}
\end{IEEEeqnarray}}
Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.

The subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved by updating the operating point with the solution from the previous update as
\begin{equation} \label{operating_point_update}
\tilde{\mbf{u}}_{l,k,n}^{(j+1)} = \tilde{\mbf{u}}_{l,k,n}^{(j)} +  \varphi^{(j)} \, (\mbf{u}_{l,k,n}^{(j+1)} - \tilde{\mbf{u}}_{l,k,n}^{(j)})
\end{equation}
where \eqn{\tilde{\mbf{u}}_{l,k,n}^{(j+1)}} is the operating point for the \eqn{\ith{j+1}} iteration, \eqn{\mbf{u}_{l,k,n}^{(j+1)}} is the optimal solution obtained in the \eqn{\ith{j}} \ac{SCA} step and \eqn{\varphi^{(j)} \in (0,1]} is the step size used to update the operating point \cite{scutari_1}. The iterative algorithm, referred as \acl{QM} \ac{JSFRA} scheme, is outlined in Algorithm \ref{algo-1}. To find a solution, we first generate transmit beamformers \eqn{\tilde{\mbf{m}}} satisfying the total power constraints \eqref{eqn-9.1d}. Then the initial values for receivers \eqn{\tilde{\mbf{w}}} are computed using \eqref{eqn-10}. Finally the initial values for \me{\tilde{\mbf{\beta}}} are obtained by \eqref{eqn-9.1c}. Note that the initial values for \eqn{p} and \eqn{q} are defined based on \eqref{eqn-wsrm-expr}. For fixed receivers \me{\tilde{\mbf{w}}}, the \ac{SCA} updates are carried out until convergence or for fixed number of iterations, say, \me{J_{\max}} to find a minimizer \me{\mbf{m}}. Next, the receivers are updated by either \eqref{opt-rx} or \eqref{eqn-10} using fixed \me{\tilde{\mbf{m}}}. It is carried out until convergence or for fixed number of iterations \me{I_{\max}}. The convergence analysis is given in Appendix \ref{sec-3.5}. Even though the objective sequence in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to ensure the convergence of the iterates to a \ac{KKT} point theoretically, we consider a modified objective in \eqref{mod_obj} instead of \eqref{eqn-6.1}.
\begin{comment}
\begin{algorithm}
\SetAlgoLined
\DontPrintSemicolon
\BlankLine
\SetKwInput{KwInit}{Initialize}
\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
$j = j + 1$\;
}
update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
$i = i + 1$, \me{j = 0}\;
}
\caption{Algorithm of \acs{JSFRA} scheme}
\label{algo-1} 
\end{algorithm}

\subsubsection*{Convergence}
In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
\end{subeqnarray}
where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}. The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}. It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.

### 2015-07-06 Response/Response 2/additions.tex
half cooked

\begin{enumerate}
\item We have shortened the discussions on the existing \textit{backpressure algorithm} in Section III-A.
\item Strong convexity of the objective function is emphasized in Appendix A-C.
\item Strict Monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
\item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
\item Short discussion on the choice of algorithm selection is provided 
\item Initialization of the \ac{SCA} operating point is also included in the revised manuscript
\end{enumerate}

>>>>

\begin{enumerate}
\item We have shortened the discussions on the existing \textit{backpressure algorithm} in Section III-A.
\item Strong convexity of the objective function is emphasized in Appendix A-C.
\item Strict monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
\item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
\item Discussions on the choice of algorithm selection have been provided 
\item Initialization of the \ac{SCA} operating point is also included in the revised manuscript
\end{enumerate}
